---
title: "My report"
author: "Qihong Lu"
date: "2017-01-11"
output: html_document
---


```{r chunk_options, echo = F}
knitr::opts_chunk$set(echo=F, warning=F, message=F)
```


## section header 

blablablabla

### sub section header 

blablablabla

#### sub sub section header 

blablablabla

**bold**

_italic_



###Load libraries 

don't print...

- the code (echo = F)

- the output (results = "hide")

- the message (message = F)

- the warning (warning = F)

```{r load_libraries, message = F, echo = F, results = "hide", warning= F}
rm(list=ls());
library(dplyr);library(ggplot2);
```

###Load data 
```{r load_data}
dataURL = 'http://kbroman.org/datacarp/portal_data_reduced.csv'
data = read.csv(dataURL)
```
These data have `r nrow(data)` rows and `r ncol(data)` columns 

###This is a plot for bla bla bla 
```{r plot}
data_reduced = data %>% group_by(species) %>% 
    summarize(wt_mean = mean(weight, na.rm = T), 
              hfl_mean = mean(hindfoot_length, na.rm = T),
              sample_size = n()) 
data_reduced %>%  ggplot(aes(x = wt_mean, y = hfl_mean)) + 
    geom_point(aes(color = sample_size, size = sample_size))
```


## Help
If you don't remember, click "Help -> Cheatsheet -> ..." or "Help -> Markdown quick reference"

